RAX:Efficiently Evaluating the Complexity of Porting for RISC-V

### 2024-01-30 Paper/latex1-27/paper.tex
Add files via upload

\section{Introduction}
RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.Many distribution manufacturers are actively promoting the porting of the RISC-V, for example,OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.

Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on prior knowledge of experts, and the lack of standardized evaluation criteria for software portability can lead to unreasonable development planning.Therefore, it is desirable to propose a method that automates the evaluation of porting complexity.This will enable different development teams to access software packages that are tailored to their abilities, thus assisting distribution vendors in the porting of RISC-V architecture.

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The Relationship between Score and CC}
  \label{fig:figure2}
  \Description{The Relationship between Score and CC}
\end{figure}
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

@@

\begin{table}
  \caption{Tool Effectiveness Comparison from Community Feedback}
  \label{tab:effectiveness}
  \begin{tabular}{ccccc}
    \toprule
    Porting Complexity & \multicolumn{2}{c}{Du's Tool} & \multicolumn{2}{c}{RAX} \\
     & TP & FN & TP & FN \\
    \midrule
    Low &32/37 & 5/37 & 35/37 & 2/37 \\
    Medium & 5/8 & 3/8 & 6/8 & 2/8 \\
    High & 2/6 & 4/6 & 6/6 & 0/6 \\
    \midrule
    Total & \textcolor{red}{39/51} & 12/51& \textcolor{red}{47/51} & 4/51 \\
      \bottomrule
\end{tabular}
\end{table}

@@

Chibios,u-boot are facing such a situation. Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool. Within evaluation, there are instances of inaccurate predictions. (1)In cgal project, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In PortAudio project, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code. This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that dlib project has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx project.

@@

They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software},\cite{1991Cyclomatic}.

>>>>

\section{Introduction}
RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.Many distribution manufacturers are actively promoting the porting of the RISC-V, for example,OpenEuler has joined RISC-V International organization, while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages for RISCV64\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.

Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on prior knowledge of experts, and the lack of standardized evaluation criteria for software portability can lead to unreasonable development planning.Even the developer is very familiar with the architectural code, it is impossible to accurately assess the overall workload.Therefore, it is desirable to propose a method that automates the evaluation of porting complexity.This will enable different development teams to access software packages that are tailored to their abilities, thus assisting distribution vendors in the porting of RISC-V architecture.

Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei}\cite{TAHIR2016101}\cite{Sholiq_2021}.However,code complexity metrics such as Cyclomatic Complexity are important measurements for software development and maintenance.Du et al. have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
To overcome these challenges, we propose RAX, an effective porting
complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions are as follows:
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figure2.pdf}
  \caption{The Relationship between Score and CC}
  \label{fig:figure2}
  \Description{The Relationship between Score and CC}
\end{figure}
\begin{itemize}
  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
\end{itemize}
The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors. Section 3 presents the implementation and evaluation of RAX. Section 4 and 5 presents related work and conclusions.

@@

\begin{table}
  \caption{Tool Effectiveness Comparison Based on Feedback}
  \label{tab:effectiveness}
  \begin{tabular}{ccccc}
    \toprule
    Porting Complexity & \multicolumn{2}{c}{Du's Tool} & \multicolumn{2}{c}{RAX} \\
     & TP & FN & TP & FN \\
    \midrule
    Low &32/37 & 5/37 & 35/37 & 2/37 \\
    Medium & 5/8 & 3/8 & 6/8 & 2/8 \\
    High & 2/6 & 4/6 & 6/6 & 0/6 \\
    \midrule
    Total & \textcolor{red}{39/51} & 12/51& \textcolor{red}{47/51} & 4/51 \\
      \bottomrule
\end{tabular}
\end{table}

@@

Chibios,u-boot are facing such a situation. Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool. Within evaluation, there are instances of inaccurate predictions. (1)In \href{https://github.com/CGAL/cgal}{cgal project}, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In \href{https://github.com/PortAudio/portaudio}{PortAudio project}, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code. This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that \href{https://github.com/davisking/dlib}{dlib project} has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like \href{https://github.com/apache/nuttx}{nuttx project}.

@@

They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software}\cite{1991Cyclomatic}.
